---
title: "Time Series Modelling"
author: "Kaustubh Saraf"
date: "4/19/2020"
output:
  word_document: default
  html_document: default
---
Loading packages
```{r}
library("forecast")
library(tidyverse)
library(vctrs)
library(lubridate)
library("tseries")
library(TSstudio)
```

Import data
```{r}
amazon=read.csv("C:/Users/kaustubh_14/Documents/GitHub/Time-Series/AMZN.csv")
```

```{r}
amazon$month <- as.factor(month.abb[(month(amazon$Date))])

levels(amazon$Months)

amazon$year <- as.factor(year(amazon$Date))

amazon <- amazon %>% 
  mutate(Months = fct_relevel(month,"Jan",
                              "Feb",
                              "Mar",
                              "Apr",
                              "May",
                              "Jun",
                              "Jul",
                              "Aug",
                              "Sep",
                              "Oct",
                              "Nov",
                              "Dec"))


```


Summary statistics
```{r}
summary(amazon)
```

Checking the range of Volume
```{r}
boxplot(amazon$Volume,main = "Boxplot : Vol. of Shares")
```

Checking the distribution of Volume
```{r}
hist(amazon$Volume)
```


The Series is the volume of shares sold
```{r}
amazon.vol <- amazon %>% 
                filter(year!=2020 & year!=2015) %>% 
                select (Volume) 

amazon.vol.ts<-ts(amazon.vol,frequency = 12, start = c(2016,1))

amazon.vol.ts
```
Splitting the dataset
```{r}
trainData = window(amazon.vol.ts, start=2016, end=c(2018,12))

testData = window(amazon.vol.ts, start=2019, end=c(2019,12))
```


# Vol. forecasting
```{r}
par(mfrow=c(1,3))

plot((trainData))
acf((trainData))
pacf((trainData)) 
```

```{r}
plot.ts(amazon.vol.ts)

diff1<-diff(amazon.vol.ts, lag=12)
plot.ts(diff1)
```


* The plots suggests that the series is stationary
* The PACF plot suggests that the series might be generated from MA1
* The ACF plot suggests that the series might be generated from AR1 or AR2

** Lets start with checking if the series is stationary **
# ADF Test

```{r}
adf.test(amazon.vol.ts,k=0)
```
The ADF suggests that the series is stationary and we do not need to take difference


# Model Fitting

Model1 AR1 Season=1,1,1
```{r}
arima100.111 <- arima(trainData, order=c(0,0,1), season=list(order=c(1,0,1), period=12))
arima100.111.fc <-forecast(arima100.111,h=12)

plot(arima100.111.fc)
lines(testData, col="red")
legend("topleft",lty=1,bty = "n",col=c("red","blue"),c("testData","ARIMAPred"))

forecasted.val <-forecast(arima100.111.fc,h=12)

model1.accuracy <- accuracy(forecasted.val,testData)

model1.accuracy <- data.frame(model1.accuracy)

model1.train.MAPE <- model1.accuracy[1, 'MAPE']
model1.test.MAPE <- model1.accuracy[2, 'MAPE']
```



Model with AR1
```{r}
arima100 <- arima(amazon.vol.ts,order=c(1,0,0))
arima100
checkresiduals(arima100)
```
* The model seems to fit the data well
* The ACF plot suggests that the residuals fit well
* The residuals are also normally distributed









Now we can check MA1 model
Model with MA1
```{r}
arima001 <- arima(amazon.vol.ts,order=c(0,0,1))
arima001
checkresiduals(arima001)
```
* The model seems to fit the data well
* The ACF plot suggests that the residuals fit well
* The residuals are also normally distributed


Now we can check AR1 and MA1 model
Model with AR1 and MA1

* The model seems to fit the data well
* The ACF plot suggests that the residuals fit well
* The residuals are also normally distributed


Initially we also observed a small spike at 2nd position in ACF plot suggesting that there might be AR2 component as well

Now we can check AR2 model
Model with AR2
```{r}
arima200 <- arima(amazon.vol.ts,order=c(2,0,0))
arima200
checkresiduals(arima200)
```
* The model seems to fit the data well
* The ACF plot suggests that the residuals fit well
* The residuals are also normally distributed


Let's try the auto-arima function and check the output
```{r}
auto.arima.model <- auto.arima(amazon.vol.ts)
auto.arima.model
checkresiduals(auto.arima.model)

```




AutoARIMA suggests that the model is generated from AR1 series which was our initial understanding.

Let's compare the different AIC values

The AIC metric suggests that AR1 has smallest AIC value and we go ahead with this model


# Predictions
Using the forecast function, we plot the predicted values for next 30 months
```{r}
plot(forecast(arima100,h=12))
```


# Next Steps:
* We will split the data into test and validation to tune the model performance
* Explore if VAR can be used to analyze the correlation between Closing price and Volume of shares traded
* R-Shiny app to include the filter to choose the time period





# VAR

Data Prep

Import data
```{r}
amazon=read.csv("C:/Users/kaustubh_14/Documents/GitHub/Time-Series/AMZN.csv")
```

```{r}
amazon$month <- as.factor(month.abb[(month(amazon$Date))])

levels(amazon$Months)

amazon$year <- as.factor(year(amazon$Date))

amazon <- amazon %>% 
  mutate(Months = fct_relevel(month,"Jan",
                              "Feb",
                              "Mar",
                              "Apr",
                              "May",
                              "Jun",
                              "Jul",
                              "Aug",
                              "Sep",
                              "Oct",
                              "Nov",
                              "Dec"))


```


```{r}
amazon.vol.close <- amazon %>% 
                filter(year!=2020 & year!=2015) %>% 
                transmute(Close,Open)
                
                    

amazon.vol.close.ts<-ts(amazon.vol.close,frequency = 12, start = c(2016,1))

amazon.vol.close.ts
```

Plot
```{r}
autoplot(amazon.vol.close.ts[,1:2], facets=TRUE) +
  xlab("Year") + ylab("") +
  ggtitle("Opening and Closing Price")
```

head(amazon)



```{r}
lm.fit <- lm(Close~Open,data=amazon.vol.close.ts)
summary(lm.fit)
```


```{r}
(fit <- auto.arima(amazon.vol.close.ts[,"Close"], xreg=amazon.vol.close.ts[,"Open"]))
```

```{r}
(fit <- Arima(amazon.vol.close.ts[,"Close"], order=c(1,1,0), season=list(order=c(2,1,0)), xreg=amazon.vol.close.ts[,"Open"]))
```



Plot
```{r}
checkresiduals(fit)
```

