---
title: "Time Series Modelling"
author: "Kaustubh Saraf"
date: "4/19/2020"
output: html_document
---
Loading packages
```{r}
library("forecast")
library(tidyverse)
library(vctrs)
library(lubridate)
library("tseries")
library(TSstudio)
```

Import data
```{r}
amazon=read.csv("C:/Users/kaustubh_14/Documents/GitHub/Time-Series/AMZN.csv")
```

```{r}
amazon$month <- month(amazon$Date)
amazon$year <- year(amazon$Date)
```


Summary statistics
```{r}
summary(amazon)
```

Checking the range of Volume
```{r}
boxplot(amazon$Volume,main = "Boxplot : Vol. of Shares")
```

Checking the distribution of Volume
```{r}
hist(amazon$Volume)
```


The Series is the volume of shares sold
```{r}
amazon.vol <- amazon %>% 
                select (month,year,Volume)

spread(amazon.vol,year,Volume)

stocksm <- amazon.vol %>% gather(month, Volume, -year)

amazon.vol %>% spread(month, Volume)

amazon.vol %>%
  gather(names_from = year, values_from = Volume)

amazon.vol.ts<-as.ts(amazon.vol)
```


# Vol. forecasting
```{r}
par(mfrow=c(1,3))
plot(log(amazon.vol.ts))
acf(log(amazon.vol.ts))
pacf(log(amazon.vol.ts)) 
```

* The plots suggests that the series is stationary
* The PACF plot suggests that the series might be generated from MA1
* The ACF plot suggests that the series might be generated from AR1 or AR2

** Lets start with checking if the series is stationary **
# ADF Test

```{r}
adf.test(amazon.vol.ts,k=1)
```
The ADF suggests that the series is stationary and we do not need to take difference

# Model Fitting
Model with AR1
```{r}
arima100 <- arima(amazon.vol.ts,order=c(1,0,0))
arima100
checkresiduals(arima100)
```
* The model seems to fit the data well
* The ACF plot suggests that the residuals fit well
* The residuals are also normally distributed


```{r}
amazon.vol.ts.split <- ts_split(ts.obj = amazon.vol.ts, sample.out = 12)

sr = window(series, start=1949, end=c(1956,12))
ser = window(series, start=1957, end=c(1960,12))

arima100 <- arima(training,order=c(1,0,0))

accuracy(arima100,testing)

length(USgas)

length(training)
length(testing)
```



Now we can check MA1 model
Model with MA1
```{r}
arima001 <- arima(amazon.vol.ts,order=c(0,0,1))
arima001
checkresiduals(arima001)
```
* The model seems to fit the data well
* The ACF plot suggests that the residuals fit well
* The residuals are also normally distributed


Now we can check AR1 and MA1 model
Model with AR1 and MA1
```{r}
arima101 <- arima(amazon.vol.ts,order=c(1,0,1))
arima101
checkresiduals(arima101)
```
* The model seems to fit the data well
* The ACF plot suggests that the residuals fit well
* The residuals are also normally distributed


Initially we also observed a small spike at 2nd position in ACF plot suggesting that there might be AR2 component as well

Now we can check AR2 model
Model with AR2
```{r}
arima200 <- arima(amazon.vol.ts,order=c(2,0,0))
arima200
checkresiduals(arima200)
```
* The model seems to fit the data well
* The ACF plot suggests that the residuals fit well
* The residuals are also normally distributed


Let's try the auto-arima function and check the output
```{r}
auto.arima.model <- auto.arima(amazon.vol.ts)
auto.arima.model
checkresiduals(auto.arima.model)
```

AutoARIMA suggests that the model is generated from AR1 series which was our initial understanding.

Let's compare the different AIC values
```{r}
Models <- rbind('AR1', 'MA1', 'AR1 MA1', 'AR2')

AIC <- rbind(arima100$aic,arima001$aic,arima101$aic,arima200$aic)


Summary <- data.frame(Models,AIC)
Summary
```
The AIC metric suggests that AR1 has smallest AIC value and we go ahead with this model


# Predictions
Using the forecast function, we plot the predicted values for next 30 months
```{r}
plot(forecast(arima100,h=12))
```


# Next Steps:
* We will split the data into test and validation to tune the model performance
* Explore if VAR can be used to analyze the correlation between Closing price and Volume of shares traded
* R-Shiny app to include the filter to choose the time period