---
title: "Time Series Modelling"
author: "Kaustubh Saraf"
date: "4/19/2020"
output:
  word_document: default
  html_document: default
---
Loading packages
```{r, warning=FALSE, message=FALSE}
library("forecast")
library(tidyverse)
library(vctrs)
library(lubridate)
library("tseries")
library(TSstudio)
```

Import data
```{r}
amazon <- read.csv("C:/Users/kaustubh_14/Documents/GitHub/Time-Series/AMZN.csv")
```

```{r}
amazon$month <- as.factor(month.abb[(month(amazon$Date))])

levels(amazon$Months)

amazon$year <- as.factor(year(amazon$Date))

amazon <- amazon %>% 
  mutate(Months = fct_relevel(month,"Jan",
                              "Feb",
                              "Mar",
                              "Apr",
                              "May",
                              "Jun",
                              "Jul",
                              "Aug",
                              "Sep",
                              "Oct",
                              "Nov",
                              "Dec"))

```


Summary statistics
```{r}
summary(amazon)
```

Checking the range of Volume
```{r}
boxplot(amazon$Volume,main = "Boxplot : Vol. of Shares")
```

Checking the distribution of Volume
```{r}
hist(amazon$Volume)
```


The Series is the volume of shares sold
```{r}
amazon.vol <- amazon %>% 
                filter(year!=2020 & year!=2015) %>% 
                select (Volume) 

amazon.vol.ts<-ts(amazon.vol,frequency = 12, start = c(2016,1))

amazon.vol.ts
```
Splitting the dataset
```{r}
trainData = window(amazon.vol.ts, start=2016, end=c(2018,12))

testData = window(amazon.vol.ts, start=2019, end=c(2019,12))
```


# Vol. forecasting
```{r}
par(mfrow=c(1,3))

plot((amazon.vol.ts))
acf((amazon.vol.ts))
pacf((amazon.vol.ts)) 
```

```{r}
plot.ts(amazon.vol.ts)

diff1<-diff(amazon.vol.ts, lag=12)
plot.ts(diff1)
```


* The plots suggests that the series is stationary
* The PACF plot suggests that the series might be generated from MA1
* The ACF plot suggests that the series might be generated from AR1 or AR2

** Lets start with checking if the series is stationary **
# ADF Test

```{r}
adf.test(amazon.vol.ts,k=0)
```
The ADF suggests that the series is stationary and we do not need to take difference


# Model Fitting

Model1 MA1 Season=1,0,0
```{r}
ma1.100 <- arima(trainData, order=c(0,0,1), season=list(order=c(1,0,0), period=12))
ma1.100.fc <-forecast(ma1.100,h=12)

plot(ma1.100.fc)
lines(testData, col="red")
legend("topleft",lty=1,bty = "n",col=c("red","blue"),c("Test Data","ARIMA Predicted"))

forecasted.val11 <-forecast(ma1.100.fc,h=12)

model1.accuracy11 <- accuracy(forecasted.val11,testData)

model1.accuracy11 <- data.frame(model1.accuracy11)

model1.train.MAPE11 <- model1.accuracy11[1, 'MAPE']
model1.test.MAPE11 <- model1.accuracy11[2, 'MAPE']
```

Model1 MA1 Season=1,0,1
```{r}
ma1.101 <- arima(trainData, order=c(0,0,1), season=list(order=c(1,0,1), period=12))
ma1.101.fc <-forecast(ma1.101,h=12)

plot(ma1.101.fc)
lines(testData, col="red")
legend("topleft",lty=1,bty = "n",col=c("red","blue"),c("Test Data","ARIMA Predicted"))

forecasted.val <-forecast(ma1.101.fc,h=12)

model1.accuracy <- accuracy(forecasted.val,testData)

model1.accuracy <- data.frame(model1.accuracy)

model1.train.MAPE <- model1.accuracy[1, 'MAPE']
model1.test.MAPE <- model1.accuracy[2, 'MAPE']
```
Model1 MA2 Season=1,0,1
```{r}
ma2.101 <- arima(trainData, order=c(0,0,2), season=list(order=c(1,0,1), period=12))
ma2.101.fc <-forecast(ma2.101,h=12)

plot(ma2.101.fc)
lines(testData, col="red")
legend("topleft",lty=1,bty = "n",col=c("red","blue"),c("Test Data","ARIMA Predicted"))

forecasted.val1 <-forecast(ma2.101.fc,h=12)

model1.accuracy1 <- accuracy(forecasted.val1,testData)

model1.accuracy1 <- data.frame(model1.accuracy1)

model1.train.MAPE1 <- model1.accuracy1[1, 'MAPE']
model1.test.MAPE1 <- model1.accuracy1[2, 'MAPE']
```
Model1 MA2 Season=1,0,2
```{r}
ma2.102 <- arima(trainData, order=c(0,0,2), season=list(order=c(1,0,2), period=12))
ma2.102.fc <-forecast(ma2.102,h=12)

plot(ma2.102.fc)
lines(testData, col="red")
legend("topleft",lty=1,bty = "n",col=c("red","blue"),c("Test Data","ARIMA Predicted"))

forecasted.val2 <-forecast(ma2.102.fc,h=12)

model1.accuracy2 <- accuracy(forecasted.val2,testData)

model1.accuracy2 <- data.frame(model1.accuracy2)

model1.train.MAPE2 <- model1.accuracy2[1, 'MAPE']
model1.test.MAPE2 <- model1.accuracy2[2, 'MAPE']
```
Model1 MA2 Season=1,1,2
```{r}
ma2.112 <- arima(trainData, order=c(0,0,2), season=list(order=c(1,1,2), period=12))
ma2.112.fc <-forecast(ma2.112,h=12)

plot(ma2.112.fc)
lines(testData, col="red")
legend("topleft",lty=1,bty = "n",col=c("red","blue"),c("Test Data","ARIMA Predicted"))

forecasted.val3 <-forecast(ma2.112.fc,h=12)

model1.accuracy3 <- accuracy(forecasted.val3,testData)

model1.accuracy3 <- data.frame(model1.accuracy3)

model1.train.MAPE3 <- model1.accuracy3[1, 'MAPE']
model1.test.MAPE3 <- model1.accuracy3[2, 'MAPE']
```



AutoArima
```{r}
auto.arima.model <- auto.arima(trainData)
auto.arima.model.fc <-forecast(auto.arima.model,h=12)

plot(auto.arima.model.fc)
lines(testData, col="red")
legend("topleft",lty=1,bty = "n",col=c("red","blue"),c("Test Data","ARIMA Predicted"))

forecasted.val4 <-forecast(auto.arima.model,h=12)

model1.accuracy4 <- accuracy(forecasted.val4,testData)

model1.accuracy4 <- data.frame(model1.accuracy4)

model1.train.MAPE4 <- model1.accuracy4[1, 'MAPE']
model1.test.MAPE4 <- model1.accuracy4[2, 'MAPE']
```


AutoARIMA suggests that the model is generated from AR1 series which was our initial understanding.

Let's compare the different AIC values
```{r}

train.mape <- c(model1.train.MAPE11, model1.train.MAPE, model1.train.MAPE1, 
                model1.train.MAPE2, model1.train.MAPE3,model1.train.MAPE4)
test.mape <- c(model1.test.MAPE11, model1.test.MAPE, model1.test.MAPE1, 
               model1.test.MAPE2, model1.test.MAPE3,model1.test.MAPE4)

mape <- data.frame(train.mape, test.mape)

rownames(mape) <- c("ma1.100","ma1.101", "ma2.101", "ma2.102", "ma2.112","Auto Arima")

mape

```
The AIC metric suggests that MA1 with seasonality AR=1 has smallest out of sample MAPE hence we go ahead with this model.


Residual Diagonastics of the Best Model
Let's try the auto-arima function and check the output
```{r}
checkresiduals(ma1.100)
```


# VAR

Data Prep

```{r}
amazon.vol.close <- amazon %>% 
                filter(year!=2020 & year!=2015) %>% 
                transmute(Close,Open)
                
                    

amazon.vol.close.ts<-ts(amazon.vol.close,frequency = 12, start = c(2016,1))

amazon.vol.close.ts
```

Plot
```{r}
autoplot(amazon.vol.close.ts[,1:2], facets=TRUE) +
  xlab("Year") + ylab("") +
  ggtitle("Opening and Closing Price")
```


```{r}
lm.fit <- lm(Close~Open,data=amazon.vol.close.ts)
summary(lm.fit)
```


```{r}
(fit <- auto.arima(amazon.vol.close.ts[,"Close"], xreg=amazon.vol.close.ts[,"Open"]))
```

```{r}
(fit <- Arima(amazon.vol.close.ts[,"Close"], order=c(1,1,0), season=list(order=c(2,1,0)), xreg=amazon.vol.close.ts[,"Open"]))
```



Plot
```{r}
checkresiduals(fit)
```

